---
output: 
  pdf_document:
    latex_engine: xelatex
    citation_package: "biblatex"
    template: "./cv-simple.tex"
    md_extensions: "-autolink_bare_uris -auto_identifiers"

name: "Li Chuin Chong"

title: "Ph.D. Candidate"
affiliation: "TWINCORE GmbH c/o HZI \\hspace{.05in} \\textbullet \\hspace{.05in} Hannover Medical School (MHH)"
contact:
  - text: "lichuinchong@twincore.de"
    link: "mailto:lichuinchong@twincore.de"
    icon: "Envelope"
    opts: "regular"
    mono: false
  - text: "Website"
    link: "https://chonglc.github.io/"
    icon: "Globe"
    mono: true
  - text: "ChongLC"
    link: "https://github.com/ChongLC"
    icon: "Github"
    mono: true
  - text: "0000-0002-3574-1365"
    link: "https://orcid.org/my-orcid?orcid=0000-0002-3574-1365"
    acad: "Orcid"
    mono: true
    
bibs:
  - "pubbed.bib"
  - "conferences.bib"
  - "inprogress.bib"
  - "review.bib"
  - "press.bib"

namehash: "7ee2eb84ac3fb6ae0cc177587fcaff6a"

raggedright: true

colorlinks: true
linkcolor: "blue"
urlcolor: "magenta"
---

```{r setup, echo = FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, comment = "")

library(RefManageR)
library(jtools)
print_refs <- function(file, names = NULL) {
  refs <- ReadBib(file, check = FALSE)
  cat(paste0("\\fullcitebib{", paste(
      c(names(refs) %just% names, names(sort(refs, sorting = "ydnt")) %not% names), 
      collapse = ", "), "}"
    )
  )
}
```

# Current Appointments

## TWINCORE Centre for Experimental and Clinical Infection Research \normalfont c/o Helmholtz Centre for Infection Research (HZI) | \normalfont Hannover, DE

### Institute for Experimental Virology

\vspace{-.05in}

* Doctoral Researcher \hfill Apr 2022 - Present

# Education

## Hannover Medical School | \normalfont Hannover Biomedical Research School, Germany

* Ph.D., Biomedical Data Science \hfill Apr 2022 - Present
  * Supervisory committee: Chris Lauber (main), Stefan Seitz, Alice Mc Hardy, Daniel P. Depledge

## Perdana University | \normalfont School of Data Sciences, Malaysia

* M.Sc. by Research, Bioinformatics \hfill 2020
  * Dissertation: Mapping the minimal set of the viral peptidome 
  * Awarded with Distinction
  * Supervisory committee: Asif M. Khan (main), Sy Bing Choi, Kenneth Ban Hon Kim
 
## Universiti Putra Malaysia | \normalfont Faculty of Medicine and Health Sciences, Malaysia

* B.Sc., Biomedical Sciences \hfill 2018
  * Dissertation: Expression, purification and characterisation of the protruding domain of \textit{Macrobrachium rosenbergii} nodavirus capsid protein
  * Supervisory committee: Kok Lian Ho, Abdah MD Akim
    

# Professional Experience
## Visiting Research Fellow \normalfont \hfill Sep 2023 - Present
  GISAID EpiArbo\texttrademark

## Visiting Trainee \normalfont \hfill Oct - Nov 2023
  Division of Virus Associated Carcinogenesis (F170), German Cancer Research Center (DKFZ), Germany

## Research Intern \normalfont \hfill May 2020 - Dec 2021
  Faculty of Medical Technology, Mahidol University, Thailand
  
## International Visiting Researcher \normalfont \hfill Feb - Sep 2021  
  Beykoz Institute of Life Sciences and Biotechnology (BILSAB), Bezmialem Vakif University, Turkey
  
## Research Assistant \normalfont \hfill Sep - Dec 2020
  Faculty of Dentistry, University of Malaya, Malaysia \& Cancer Research Malaysia

  
# Publications

```{r results = 'asis'}
print_refs <- function(file, names = NULL) {
  refs <- ReadBib(file, check = FALSE)
  cat(paste0("\\fullcitebib{", paste(
      c(names(refs) %just% names, names(sort(refs, sorting = "ydnt")) %not% names), 
      collapse = ", "), "}"
    )
  )
}
print_refs("pubbed_no_ann.bib")
```

# Book Chapters

```{r results='asis'}
print_refs("books.bib")
```

# Software

### \textbf{UNIQmin}: An alignment-independent tool for the study of pathogen sequence diversity at any given rank of taxonomy lineage
\small \vspace{-.05in}
* \faPython \ [PyPi](https://pypi.org/project/uniqmin/)
\hspace{.03in} \textbullet \hspace{.05in} 
\faGithub \hspace{.02in} [UNIQmin](https://github.com/ChongLC/MinimalSetofViralPeptidome-UNIQmin)
* Role: Developer (main) and maintainer

\normalsize 
### \textbf{vDiveR}: A graphical user interface (GUI)-based web application hosted on R Shiny for the visualization of various diversity dynamics
\small \vspace{-.05in}
* \faRProject \ [CRAN](https://cran.r-project.org/web/packages/vDiveR/index.html) 
\hspace{.03in} \textbullet \hspace{.05in} 
\faGithub \hspace{.02in} [vDiveR](https://github.com/pendy05/DiveR)
* Role: Domain expert


# Presentations 

## Invited talks

\normalsize

Unravelling the virosphere: Insights from viral discovery and sequence diversity analysis 

\vspace{-.07in} \hfill \small 17 Jun 2023 \thinspace

\phantom{.5in} \textbullet{} \small Guest Lecture series of Indonesian Medical Education and Research Institute (IMERI)

## Contributed talks

\normalsize

A near-full compression of SARS-CoV-2 peptidome using UNIQmin 

\vspace{-.07in} \hfill \small 12-21 Sep 2022 \thinspace

\phantom{.5in} \textbullet{} \small 21st European Conference on Computational Biology (ECCB2022), Stiges, Barcelona
  
\phantom{.5in} \textbullet{} \small GOBLET Fund & Malaysia Trust Fund Travel Fellowship Award

\normalsize

Identification of highly conserved, serotype-specific dengue virus sequences: Implications for vaccine design 

\vspace{-.07in}  \hfill \small 10-12 Sep 2019 \thinspace

\phantom{.5in} \textbullet{} \small 18th International Conference on Bioinformatics (InCoB 2019), Jakarta, Indonesia

\phantom{.5in} \textbullet{} \small APBioNET Travel Fellowship Award

## Posters

\normalsize

Identification of RNA viruses and host reservoirs with high spillover risk 

\vspace{-.07in}  \hfill \small 17-21 Oct 2022 \thinspace

\phantom{.5in} \textbullet{} EMBL-EBI: Bioinformatics approach to viruses (virtual)

\normalsize

UNIQmin, an alignment-independent tool for the study of viral sequence diversity at any given rank of taxonomy lineage: HPC solutions for big-data performance boost 

\vspace{-.07in}  \hfill \small 30 Aug-3 Sep 2021 \thinspace

\phantom{.5in} \textbullet{} 2021 ACM Europe Summer School (virtual) 

\normalsize

Mapping the minimal set of the viral peptidome across all major viral taxonomies 

\vspace{-.07in}  \hfill \small 25-30 Jul 2021 \thinspace

\phantom{.5in} \textbullet{} 29th Conference on Intelligent Systems for Molecular Biology and 20th European 
  
  \vspace{-.07in} \phantom{.5in} Conference on Computational Biology (ISMB/ECCB 2021; virtual)

\phantom{.5in} \textbullet{} ISMB/ECCB Fellowship Award

\normalsize

UNIQmin: An alignment-independent approach to generate a minimal set of viral peptidome 

\vspace{-.07in}  \hfill \small 15-16 May 2021 \thinspace

\phantom{.5in} \textbullet{} International Conference on Bioinformatics, Computational Biology, and Biomedical 
  
  \vspace{-.07in} \phantom{.5in} Science (ICBCBBS 2021; virtual)

\phantom{.5in} \textbullet{} Best E-Poster Award

\normalsize

Identification of serotype-specific, highly conserved dengue virus sequences: Implications for vaccine design

\vspace{-.07in}  \hfill \small 26-28 Sep 2018 \thinspace

\phantom{.5in} \textbullet{} 17th International Conference on Bioinformatics (InCoB 2018), New Delhi, India

\phantom{.5in} \textbullet{} ISCB Travel Fellowship Award


# Grants

## Intramural Funding

\normalsize Helmholtz Visiting Researcher Grant (€4,000) \hfill 2023 \thinspace

\phantom{.5in} \small Role: Visiting Trainee

## Extramural Funding

\normalsize PUTI Q1 Grant from Universitas Indonesia (IDR 120 million) \hfill 2022 \thinspace

\phantom{.5in} \small Role: Collaborator

\phantom{.5in} \small PI: Toar Jean Maurice Lalisang (main) & Linda Erlina (co-)

\normalsize Malaysian Medical Association (MMA) (MYR 5,000) \hfill 2019  \thinspace

\phantom{.5in} \small Role: Collaborator

\phantom{.5in} \small PI: Mohammad Asif Khan (main) & Choi Sy Bing (co-)

\normalsize


# Honors and Awards 

\textbullet{} GOBLET Fund Travel Fellowship for ECCB 2022 \thinspace

\textbullet{} Malaysia Trust Fund Travel Fellowship for ECCB 2022 \thinspace 

\textbullet{} ESCV Fellowship for ESCV 2021 \thinspace

\textbullet{} ISCB Fellowship for ISMB/ECCB 2021 \thinspace 

\textbullet{} Malaysia Trust Fund for support on publication fee for `Chong et al.(2021)` \thinspace 

\textbullet{} Best E-Poster Award, ICBCBBS 2021 \thinspace 

\textbullet{} APBioNET Travel Fellowship for InCoB 2019 \thinspace

\textbullet{} ISCB Travel Fellowship for InCoB 2018 \thinspace

\textbullet{} Public Service Department – National Degree Programme (JPA-PIDN) Scholarship for B.Sc. (Biomedical Sciences) 2015-2018 \thinspace


\newpage
\normalsize

# Teaching and Service

## Graduate Student Supervisor
\textit{Supervisor} 

  Stephen Sugiharto \hspace{.03in} \textbullet \hspace{.05in} B.Sc. (Bioinformatics), I3L, ID \hfill 2022-2023 \thinspace


<!-- \newpage -->


## Student Mentor

  Tham Hong Yun \hspace{.03in} \textbullet \hspace{.05in} Ph.D. (Microbiology), UPM, MY \hfill 2018-2024 \thinspace
  
  Sofiah binti Tajuddin \hspace{.03in} \textbullet \hspace{.05in} M.Sc. (Microbiology), UPM, MY \hfill 2019-2022 \thinspace
  
  Srosha Khanjou \hspace{.03in} \textbullet \hspace{.05in} BASc (Medicine), MUIC, TH \hfill 2020-2021 \thinspace

  Interns at CaRE UPM*  \hspace{.03in} \textbullet \hspace{.05in} B.Sc. (Biomedical Sciences), UPM, MY \hfill 2018 \thinspace
  
  \hspace{1.48in} \textbullet \hspace{.05in} B.Sc. (Biomedical Sciences), UM, MY \hfill 2018 \thinspace
  
  \scriptsize *UPM: Siti Najiha Binti Abu Bakar, Anis Zuhaida Binti Mamnun, Nor Shamira Rosdi, Muhammad Rusydie Mohd Rasid; UM: Aisyah Shamsuddin, Wardah Othman, Nurhusna Abd Samad
  
  \normalsize
  Interns at CaRE UPM*  \hspace{.03in} \textbullet \hspace{.05in} B.Sc. (Biomedical Sciences), UPM, MY \hfill 2017 \thinspace
  
  \scriptsize *UPM: Eugene Chua, Ong Si Ying, Teo Yu Yun, Lim Xin, Khor Winnie, Lok Zen Hui, Even Lim
  
\normalsize

## Outreach & Professional Societies
\textit{Leadership}

  \textbullet{} Finance Committee Member, ISCB Student Council (ISCBSC) \hfill 2023-Present \thinspace
  
  \textbullet{} Ambassador, Asia Pacific Bioinformatics Network (APBioNET) \hfill 2021-2022 \thinspace
  
  \textbullet{} Public Relations & Outreach (PRO) Committee Member, Global Organisation for Bioinformatics Learning, Education & Training (GOBLET) \hfill 2019-2021 \thinspace
  
  \textbullet{} Executive Council of Association for Medical and Bio-Informatics Singapore (AMBIS) \hfill 2018-2019 \thinspace
  
  \textbullet{} Executive Council of Alumni and Leadership of Biomedical Science Club, UPM \hfill 2015 \thinspace


# References

\begin{multicols}{2}

\textbf{Dr. Chris Lauber} \\
\textit{Head of Computational Virology} \\
Institute of Experimental Virology, TWINCORE GmbH \\
\textit{Assistant Professor} \\
RESIST Cluster of Excellence, Medizinische Hochschule Hannover (MHH) \\
Hannover, Germany \\
\href{mailto:chris.lauber@twincore.de}{chris.lauber@twincore.de}

\columnbreak

\textbf{Dr. Mohammad Asif Khan} \\
\textit{Professor and Associate Dean} \\
College of Computing and Information Technology \\
University of Doha for Science and Technology (UDST) \\
Doha, Qatar \\
\href{mailto:asif.khan@udst.edu.qa}{asif.khan@udst.edu.qa}
\end{multicols}
