---
output: 
  pdf_document:
    latex_engine: xelatex
    citation_package: "biblatex"
    template: "./cv-simple.tex"
    md_extensions: "-autolink_bare_uris -auto_identifiers"

name: "Li Chuin Chong"

title: "Ph.D. Candidate"
affiliation: "TWINCORE GmbH c/o HZI \\hspace{.05in} \\textbullet \\hspace{.05in} Hannover Medical School"
contact:
  - text: "lichuinchong@twincore.de"
    link: "mailto:lichuinchong@twincore.de"
    icon: "Envelope"
    opts: "regular"
    mono: false
#  - text: "Website"
#    link: "https://chonglc.github.io/"
#    icon: "Globe"
#    mono: true
  - text: "ChongLC"
    link: "https://github.com/ChongLC"
    icon: "Github"
    mono: true
  - text: "0000-0002-3574-1365"
    link: "https://orcid.org/my-orcid?orcid=0000-0002-3574-1365"
    acad: "Orcid"
    mono: true
photo: "profile-img-compressed.jpg"
    
bibs:
  - "pubbed.bib"
  - "conferences.bib"
  - "inprogress.bib"
  - "review.bib"
  - "press.bib"

namehash: "7ee2eb84ac3fb6ae0cc177587fcaff6a"

raggedright: true

colorlinks: true
linkcolor: "blue"
urlcolor: "magenta"
---

```{r setup, echo = FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, comment = "")

library(RefManageR)
library(jtools)
print_refs <- function(file, names = NULL) {
  refs <- ReadBib(file, check = FALSE)
  cat(paste0("\\fullcitebib{", paste(
      c(names(refs) %just% names, names(sort(refs, sorting = "ydnt")) %not% names), 
      collapse = ", "), "}"
    )
  )
}
```

# Summary
<!-- An enthusiastic scientist with a profound interest in viral evolution and the application of vaccine design. Given the importance of bioinformatics in biomedical science research, I began my transition from bench-work to bioinformatics since 2017. I am interested in better understanding how vaccines/drugs work towards a more effective prevention/clearance of viral diseases, and how to overcome diseases with no or lack of an effective prophylactic or therapeutic intervention. Currently, my focus is on assessing the spillover risks and patterns that contribute to the pandemic potential of RNA viruses. -->

Computational virologist working at the interface of viral evolution, large-scale sequence analysis, and data-driven approaches in computational biology. My research focuses on understanding viral diversity and emergence using high-throughput sequencing data. I develop scalable computational approaches for virus discovery, diversity analysis, and spillover risk assessment, with a particular interest in quantitative and integrative frameworks for studying viral evolution.

Currently, I am a PhD candidate in Biomedical Data Science at Hannover Medical School (TWINCORE), where my work is associated with the COVIPA consortium focused on understanding virological and immunological drivers of COVID-19 pathogenesis.
\thinspace

\small Virus evolution \hspace{.03in} \textbullet \hspace{.03in} Virus discovery \hspace{.03in} \textbullet \hspace{.03in} Spillover risk assessment


# Current Appointments

## TWINCORE Centre for Experimental and Clinical Infection Research \normalfont c/o Helmholtz Centre for Infection Research (HZI) | \normalfont Hannover, DE

### Institute for Experimental Virology

\vspace{-.05in}

- Doctoral Researcher \hfill Apr 2022 - Present

# Education

## Hannover Medical School | \normalfont Hannover Biomedical Research School, Germany

- \textbf{Ph.D.}, Biomedical Data Science \hfill Apr 2022 - Present
  - Project title: Increasing pandemic preparedness by computational high-throughput virus discovery: Identification of RNA viruses and host reservoirs with high spillover risk
  - Supervisory committee: Chris Lauber (main), Stefan Seitz, Alice McHardy, Daniel P. Depledge

## Perdana University | \normalfont School of Data Sciences, Malaysia

- \textbf{MRes}, Bioinformatics \hfill 2020
  - Dissertation: Mapping the minimal set of the viral peptidome 
  - Awarded with Distinction (the highest)
  - Supervisory committee: Asif M. Khan (main), Sy Bing Choi, Kenneth Ban Hon Kim
 
## Universiti Putra Malaysia | \normalfont Faculty of Medicine and Health Sciences, Malaysia

- \textbf{B.Sc.}, Biomedical Sciences \hfill 2018
  - Dissertation: Expression, purification and characterisation of the protruding domain of \textit{Macrobrachium rosenbergii} nodavirus capsid protein
  - Supervisory committee: Kok Lian Ho, Abdah MD Akim
    

# Professional Experience
## Doctoral Researcher \normalfont \hfill Apr 2022 - Present
  Institute for Experimental Virology, TWINCORE Centre for Experimental and Clinical Infection Research \normalfont c/o Helmholtz Centre for Infection Research (HZI), Germany

## Visiting Trainee \normalfont \hfill Oct - Nov 2023
  Division of Virus Associated Carcinogenesis (F170), German Cancer Research Center (DKFZ), Germany

\newpage
## Research Intern \normalfont \hfill May 2020 - Dec 2021
  Faculty of Medical Technology, Mahidol University, Thailand
  
## International Visiting Researcher \normalfont \hfill Feb - Sep 2021  
  Beykoz Institute of Life Sciences and Biotechnology (BILSAB), Bezmialem Vakif University, Turkey
  
## Research Assistant \normalfont \hfill Sep - Dec 2020
  Faculty of Dentistry, University of Malaya, Malaysia \& Cancer Research Malaysia

## Research Assistant \normalfont \hfill Dec 2019 - May 2020
  Perdana University School of Data Sciences (PU-ScDS), Malaysia
  

# Skills
## Experimental Techniques (previously used)
- **Molecular and structural biology**: DNA/plasmid extraction, PCR, protein expression and purification, electrophoresis, western blotting, chromatography (IMAC, FPLC), protein characterisation (CD, DLS)
- **_In vivo_ techniques**: Laboratory animal handling, dissection, and phlebotomy

## Bioinformatics
- **Comparative genomics & Phylogenetics**: Multiple sequence alignment, phylogenetic analysis, sequence clustering, evolutionary analysis
- **Vaccine informatics & Immunoinformatics**: Entropy-based quantitative analysis, motif identification analysis, diversity analysis, immune-relevance analysis
- **Structural bioinformatics**: Protein and RNA structure annotation, structural visualisation (PyMOL, UCSF Chimera, VMD), secondary structure prediction, protein structure analysis, protein-protein docking and interaction analysis
- **Viral informatics & Metagenomics**: Viral genome annotation, SRA-based virus discovery, metagenomic virome profiling (Taxonomic chracterization of viromes, Abundance estimation of viral population), host-pathogen interaction analysis
- **High performance computing (HPC) environments**: PBS, SLURM
- **Workflow automation and management**: Snakemake

## Data Science
- Exploratory data analysis, data visualisation, biostatistics, web scraping, application development

## Web Development
- HTML, CSS, JavaScript

## Programming Languages (intermediate)
- Python, R, shell scripting, GitHub CI/CD pipeline



# Publications
**Citations:** 395 | **h-index:** 11 | **Papers Published:** 25

### For a complete list of publications, please visit my [Google Scholar profile](https://scholar.google.com/citations?user=NSDlr5IAAAAJ&hl=en).

\vspace{0.3cm}

\textbf{Chong et al.} Quantifying Zoonotic Spillover Risk: Identifying High Risk RNA Viruses with PREDICTORix. \textit{Manuscript in preparation.}

\vspace{0.35cm}

\noindent\textit{(selected; \textsuperscript{*}co-first author)}

\vspace{0.3cm}
```{r results = 'asis'}
print_refs <- function(file, names = NULL) {
  refs <- ReadBib(file, check = FALSE)
  cat(paste0("\\fullcitebib{", paste(
      c(names(refs) %just% names, names(sort(refs, sorting = "ydnt")) %not% names), 
      collapse = ", "), "}"
    )
  )
}
print_refs("pubbed_no_ann.bib")
```

# Book Chapters

```{r results='asis'}
print_refs("books.bib")
```

# Software

### \textbf{PREDICTORix}: A scalable, phylogeny-aware pipeline for quantifying RNA virus spillover risk
\small \vspace{-.05in}
* \faGithub \hspace{.02in} PREDICTORix (private mode) \hspace{.03in} \textbullet \hspace{.05in} Developer (main)

\normalsize 
### \textbf{UNIQmin}: An alignment-independent tool for the study of pathogen sequence diversity at any given rank of taxonomy lineage
\small \vspace{-.05in}
* \faPython \ [PyPi](https://pypi.org/project/uniqmin/)
\hspace{.03in} \textbullet \hspace{.05in} 
\faGithub \hspace{.02in} [UNIQmin](https://github.com/ChongLC/MinimalSetofViralPeptidome-UNIQmin) \hspace{.03in} \textbullet \hspace{.05in} Developer (main) and maintainer

\normalsize 
### \textbf{vDiveR}: A graphical user interface (GUI)-based web application hosted on R Shiny for the visualization of various diversity dynamics
\small \vspace{-.05in}
* \faRProject \ [CRAN](https://cran.r-project.org/web/packages/vDiveR/index.html) 
\hspace{.03in} \textbullet \hspace{.05in} 
\faGithub \hspace{.02in} [vDiveR](https://github.com/pendy05/DiveR) \hspace{.03in} \textbullet \hspace{.05in} Co-developer

\normalsize 
### \textbf{VirusHunterGatherer}: A Snakemake pipeline for data-driven virus discovery
\small \vspace{-.05in}
* \faGithub \hspace{.02in} [VirusHunterGatherer](https://github.com/lauberlab/VirusHunterGatherer) \hspace{.03in} \textbullet \hspace{.05in} Contributor

\normalsize 
### \textbf{Virusparies}: An R package designed for visualizing outputs from VirusHunterGatherer
\small \vspace{-.05in}
* \faGithub \hspace{.02in} [Virusparies](https://github.com/SergejRuff/Virusparies) \hspace{.03in} \textbullet \hspace{.05in} Contributor

# Grants

## Intramural Funding

\normalsize Helmholtz Visiting Researcher Grant (€4,000) \hfill 2023 \thinspace

\phantom{.5in} \small Role: Visiting Trainee

## Extramural Funding

\normalsize PUTI Q1 Grant from Universitas Indonesia (IDR 120 million) \hfill 2022 \thinspace

\phantom{.5in} \small Role: Collaborator \hspace{.03in} | \hspace{.05in} PI: Toar Jean Maurice Lalisang (main) & Linda Erlina (co-)

\normalsize Malaysian Medical Association (MMA) (MYR 5,000) \hfill 2019  \thinspace

\phantom{.5in} \small Role: Collaborator \hspace{.03in} | \hspace{.05in} PI: Mohammad Asif Khan (main) & Choi Sy Bing (co-)

\normalsize

<!-- \newpage -->
<!-- \normalsize -->
\newpage


# Teaching and Service

## Graduate Student Supervisor
\textit{Supervisor} 

  Stephen Sugiharto \hspace{.03in} \textbullet \hspace{.05in} B.Sc. (Bioinformatics), I3L, ID \hfill 2022-2023 \thinspace


<!-- \newpage -->


## Student Mentor

  Pendy Tok \hspace{.03in} \textbullet \hspace{.05in} MRes (Bioinformatics), UM, MY \hfill 2021-Present \thinspace
  
  Sergej Ruff \hspace{.03in} \textbullet \hspace{.05in} M.Sc. (Biomedical Data Science), MHH, DE \hfill 2024 \thinspace
  
  Tham Hong Yun \hspace{.03in} \textbullet \hspace{.05in} Ph.D. (Microbiology), UPM, MY \hfill 2018-2024 \thinspace
  
  Sofiah binti Tajuddin \hspace{.03in} \textbullet \hspace{.05in} MRes (Microbiology), UPM, MY \hfill 2019-2022 \thinspace
  
  Interns and student volunteers at BVU  \hspace{.03in} \textbullet \hspace{.05in} Beykoz Institute of Life Sciences and Biotechnology (BILSAB), TR \hfill 2021 \thinspace
  
  Srosha Khanjou \hspace{.03in} \textbullet \hspace{.05in} BASc (Medicine), MUIC, TH \hfill 2020-2021 \thinspace

  Interns at CaRE UPM  \hspace{.03in} \textbullet \hspace{.05in} B.Sc. (Biomedical Sciences), UPM, MY \hfill 2017-2018 \thinspace
  
  \hspace{1.42in} \textbullet \hspace{.05in} B.Sc. (Biomedical Sciences), UM, MY \hfill 2018 \thinspace
  
\normalsize

## Outreach & Professional Societies
\textit{Leadership}

  \textbullet{} Finance Committee Member, ISCB Student Council (ISCBSC) \hfill 2023-Present \thinspace
  
  \textbullet{} Organizing Committee Member, APBioNETTalks \hfill 2020-2023 \thinspace
  
  \textbullet{} Ambassador, Asia Pacific Bioinformatics Network (APBioNET) \hfill 2021-2022 \thinspace
  
  \textbullet{} Public Relations & Outreach (PRO) Committee Member, Global Organisation for Bioinformatics Learning, Education & Training (GOBLET) \hfill 2019-2021 \thinspace
  
  \textbullet{} Executive Council of Association for Medical and Bio-Informatics Singapore (AMBIS) \hfill 2018-2019 \thinspace
  
  \textbullet{} Executive Council of Alumni and Leadership of Biomedical Science Club, UPM \hfill 2015


# Presentations 

## Keynote/Invited talks

\normalsize

An overview of the RNA virus discovery field since the 2023 RdRp Summit! 

\vspace{-.07in} \hfill \small 11-12 May 2025 \thinspace

\phantom{.5in} \textbullet{} \small RdRp Summit 2025, Lisbon, Portugal

\normalsize

Unravelling the virosphere: Insights from viral discovery and sequence diversity analysis 

\vspace{-.07in} \hfill \small 17 Jun 2023 \thinspace

\phantom{.5in} \textbullet{} \small Guest Lecture series of Indonesian Medical Education and Research Institute (IMERI)

## Contributed talks

\normalsize

PREDICTORix: A scalable phylogeny-aware approach for quantifying viral spillover risk 

\vspace{-.07in} \hfill \small 11-12 May 2025 \thinspace

\phantom{.5in} \textbullet{} \small RdRp Summit 2025, Lisbon, Portugal

<!--\newpage-->
\normalsize

A near-full compression of SARS-CoV-2 peptidome using UNIQmin 

\vspace{-.07in} \hfill \small 12-21 Sep 2022 \thinspace

\phantom{.5in} \textbullet{} \small 21st European Conference on Computational Biology (ECCB2022), Stiges, Barcelona

\normalsize

Identification of highly conserved, serotype-specific dengue virus sequences: Implications for vaccine design 

\vspace{-.07in}  \hfill \small 10-12 Sep 2019 \thinspace

\phantom{.5in} \textbullet{} \small 18th International Conference on Bioinformatics (InCoB 2019), Jakarta, Indonesia

\newpage
## Posters \small\textit{(selected)}

\normalsize

PREDICTORix: A scalable phylogeny-aware approach for quantifying viral spillover risk

\vspace{-.07in}  \hfill \small 13-15 May 2025 \thinspace

\phantom{.5in} \textbullet{} International Virus Bioinformatics Meeting (ViBioM 2025), Lisbon, Portugal

\normalsize

Towards quantifying zoonotic spillover risks of RNA viruses: A comprehensive approach using next-generation sequencing data

\vspace{-.07in}  \hfill \small 16-20 Sep 2024 \thinspace

\phantom{.5in} \textbullet{} 23rd European Conference on Computational Biology (ECCB 2024), Turku, Finland

\normalsize

UNIQmin, an alignment-independent tool for the study of viral sequence diversity at any given rank of taxonomy lineage: HPC solutions for big-data performance boost 

\vspace{-.07in}  \hfill \small 30 Aug-3 Sep 2021 \thinspace

\phantom{.5in} \textbullet{} 2021 ACM Europe Summer School (virtual) 

\normalsize

Mapping the minimal set of the viral peptidome across all major viral taxonomies 

\vspace{-.07in}  \hfill \small 25-30 Jul 2021 \thinspace

\phantom{.5in} \textbullet{} 29th Conference on Intelligent Systems for Molecular Biology and 20th European 
  
  \vspace{-.07in} \phantom{.5in} Conference on Computational Biology (ISMB/ECCB 2021; virtual)



# Honors and Awards
\vspace{0.35cm}

\noindent\textit{(selected)}

\textbullet{} MHH Congress Scholarship & ISME Travel Fellowship – Oral & Poster presentation, 2nd RdRp Summit & ViBioM2025 \thinspace

\textbullet{} Best Project Award, Collaborative Bioinformatics Hackathon 2025: Machine learning and AI approaches to multimodal problems in computational biology \thinspace

\textbullet{} OBF Travel Fellowship – Poster presentation, ECCB 2024 \thinspace

\textbullet{} GOBLET Fund & Malaysia Trust Fund Travel Fellowship – Oral presentation, ECCB 2022 \thinspace

\textbullet{} First Prize, BCM/HGSC Virtual Hackathon 2021: Pan-structural Variation in the Cloud \thinspace

\textbullet{} ESCV Fellowship – Poster presentation, ESCV 2021 \thinspace

\textbullet{} ISCB Fellowship – Poster presentation, ISMB/ECCB 2021 \thinspace 

\textbullet{} Best E-Poster Award, ICBCBBS 2021 \thinspace 

\textbullet{} APBioNET Travel Fellowship – Oral presentation, InCoB 2019 \thinspace

\textbullet{} Public Service Department - National Degree Programme (JPA-PIDN) Scholarship for B.Sc. (Biomedical Sciences), 2015-2018


<!--\newpage-->
# References

\begin{multicols}{2}

\textbf{Dr. Chris Lauber} \\
\textit{Head of Computational Virology} \\
Institute of Experimental Virology, TWINCORE GmbH \\
\textit{Assistant Professor} \\
RESIST Cluster of Excellence, Medizinische Hochschule Hannover (MHH) \\
Hannover, Germany \\
\href{mailto:chris.lauber@twincore.de}{chris.lauber@twincore.de}

\vspace{1.5em} % Adjust the space between the references

\textbf{Dr. Mohammad Asif Khan} \\
\textit{Professor and Associate Dean} \\
College of Computing and Information Technology \\
University of Doha for Science and Technology (UDST) \\
Doha, Qatar \\
\href{mailto:asif.khan@udst.edu.qa}{asif.khan@udst.edu.qa}

\columnbreak

\textbf{Dr. Thomas Pietschmann} \\
\textit{Director} \\
Institute of Experimental Virology, TWINCORE GmbH \\
\textit{Professor} \\
RESIST Cluster of Excellence, Medizinische Hochschule Hannover (MHH) \\
Hannover, Germany \\
\href{mailto:thomas.pietschmann@twincore.de}{thomas.pietschmann@twincore.de}

\end{multicols}


